Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-08 paper/paper.tex
extend algorithm selection part

@@

To decide which solver to run on the remaining instances, we use LLAMA~\cite{kotthoff_llama_2013}.
In preliminary experiments, we identified random forest regression to predict the performance
difference between pairs of algorithms, with the best algorithm identified as the one with the best
cumulative performance difference over all pairs, as the best approach. We make no claims that this
is the overall best approach.

The data we use in this paper is available as Aslib scenario GRAPHS-2015.

>>>>

In addition to computing feature values, the LAD preprocessing is able to detect
whether an instance is unsatisfiable. In this case, it is not necessary to run
an algorithm on the instance.

@@

To decide which solver to run on the remaining instances, we use
LLAMA~\cite{kotthoff_llama_2013}. LLAMA supports the most common algorithm
selection approaches used in the literature. We performed a set of preliminary
experiments to determine the approach that works best in this case.

LLAMA's pairwise regression approach with random forest regression gave the best
performance. The idea is very similar to the pairwise classification used
in~\cite{xu_satzilla_2008}. For each pair of algorithms in our portfolio, we
train a model that predicts the performance difference between them. That is, if
the first algorithm is better than the second, the difference is positive,
otherwise negative. The algorithm with the highest cumulative performance
difference, i.e.\ the most positive difference over all other algorithms, is
chosen to be run.

As this approach gives very good performance already, we did not tune the
parameters of the random forest machine learning algorithm. It is possible that
overall performance can be improved by doing so and we make no claims that the
particular algorithm selection approach we use in this paper cannot be improved.

The data we use in this paper is available as ASlib~\cite{aslib} scenario
GRAPHS-2015.
